---
title: "BNP Project"
output: pdf_document
---

```{r load library, message=FALSE, warning=FALSE, cache=TRUE}
library(data.table)
library(FactoMineR)
library(factoextra)
library(gplots)
```

## Exploratory data analysis for BNP Porject

```{r load data, echo=FALSE, cache=TRUE}
train <- fread("train.csv")
# train[, .(target, v22, "v40-v50"=v40-v50), ]
categorical.cols <- names(train)[sapply(train, is.character)]
numerical.cols <- names(train)[sapply(train, is.numeric)][-c(1,2)]
train.cat <- train[,..categorical.cols]
train.num <- train[,..numerical.cols]
```
## Categorical variables

### Looking for correlated categorical variables(Correspondence Analysis)
```{r categorical, echo=TRUE, cache=TRUE}

correlated.cat.vars = c()
cats <- categorical.cols
for (col1 in cats) {
  cats <- cats[-1]
  for (col2 in cats) {
    tb <- train[, c(col1, col2), with=FALSE] 
    ct <- table(tb) # contingency table
    ca <- CA(ct, graph = FALSE) # correspondence analysis
    trace <- sum(ca$eig$eigenvalue) 
    if (sqrt(trace) > 1) {
      correlated.cat.vars <- rbind(correlated.cat.vars, c(col1, col2, sqrt(trace)))
    }
  }
}
correlated.cat.vars <- data.frame(correlated.cat.vars)
colnames(correlated.cat.vars) <- c("var1", "var2", "corr.coeff")
correlated.cat.vars
```

### Categorical variables: v91-v107

```{r v91-v107, message=FALSE, warning=FALSE, cache=TRUE}
# Contingency table
tab.v91.v107 <- table(train[,.(v91, v107),])
tab.v91.v107

# Draw balloon plot
balloonplot(t(tab.v91.v107), main ="Categorical variable: v91-107", xlab ="",
            ylab="", label = FALSE,  show.margins = FALSE)

# Chi-squared test
chisq.test(tab.v91.v107)

# Correspondence analysis(CA)
ca.v91.v107 <-  CA(tab.v91.v107, graph=TRUE)
summary(ca.v91.v107, nb.dec = 2, ncp = 2)

```

These two variables are duplicates. Just keep one of them.

### Categorical variables: v47-v110

```{r cache=TRUE}
# Contingency table
tab.v47.v110 <- table(train[,.(v47, v110),])
tab.v47.v110

# Draw balloon plot
balloonplot(t(tab.v47.v110), main ="Categorical variable: v91-107", xlab ="", 
            ylab="", label = FALSE,  show.margins = FALSE)

# Chi-squared test
chisq.test(tab.v47.v110)

# Correspondence analysis(CA)
ca.v47.v110 <-  CA(tab.v47.v110, graph=TRUE)
summary(ca.v47.v110, nb.dec = 2, ncp = 2)

```

### Categorical variables: v71-v75

```{r cache=TRUE}
# Contingency table
tab.v71.v75 <- table(train[,.(v71, v75),])
tab.v71.v75

# Draw balloon plot
balloonplot(t(tab.v71.v75), main ="Categorical variable: v71-75", xlab ="", 
            ylab="", label = FALSE,  show.margins = FALSE)

# Chi-squared test
chisq.test(tab.v71.v75)

# Correspondence analysis(CA)
ca.v71.v75 <-  CA(tab.v71.v75, graph=TRUE)
summary(ca.v71.v75, nb.dec = 2, ncp = 2)
```


```{r echo=FALSE, cache=TRUE}
library(ggplot2)
v71 = data.frame(table(train[, v71,]))
ggplot(v71, aes(x=reorder(Var1, -Freq), y=Freq)) + 
  geom_bar(stat="identity", fill="seagreen") +
  labs(x="", y="Count", title="Categorical variable v71")

v75 = data.frame(table(train[, v75,]))
ggplot(v75, aes(x=reorder(Var1, -Freq), y=Freq)) + 
  geom_bar(stat="identity", fill="seagreen") +
  labs(x="", y="Count", title="Categorical variable v75")

```

### Categorical varibles: v71-v79

```{r cache=TRUE}
# Contingency table
tab.v71.v79 <- table(train[,.(v71, v79),])
tab.v71.v79

# Draw balloon plot
balloonplot(t(tab.v71.v79), main ="Categorical variable: v71-79", xlab ="", 
            ylab="", label = FALSE,  show.margins = FALSE)

```

## Numerical variables

### Dealing with missing values
```{r cache=TRUE}
library(caret)
library(mice)

# Pattern of missing values
md.pattern(train.num)

# Imputing missing values with mean
impute.mean <- function(x) {
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
}
imputed.train.num <- train.num[, lapply(.SD, impute.mean)]
imputed.train.num

findLinearCombos(imputed.train.num)$linearCombos # Remove 110
findLinearCombos(imputed.train.num[,c(-110),])
```


## References:
1. http://www.sthda.com/english/wiki/correspondence-analysis-in-r-the-ultimate-guide-for-the-analysis-the-visualization-and-the-interpretation-r-software-and-data-mining#correspondence-analysis-ca

